### 2024-05-14 index.qmd
20240514 - update

@@

@@

>>>>

The following code chunk throws an error if I remove it:

```{r}
1 + 1
```

@@

<!--
[![DOI](images/zenodo_doiBadge.png)](https://doi.org/10.5281/zenodo.6466589)
-->

@@

```
@book{petersenFantasyFootballAnalytics,
  title = {Fantasy football analytics},
  author = {Petersen, Isaac T.},
  year = {2024},
  publisher = {{University of Iowa Libraries}},
  note = {Version 0.0.1},
  doi = {INSERT},
  isbn = {INSERT},
  url = {https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook}
}
```
